Predicting The Success of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics Using Mean and Standard Deviation Derived Parameters

### 2024-01-09 manuscript/submission.tex
testing quotation revision

To predict which of the United States athletes are most likely to medal on the various apparatuses, 
I will be using the cleaned data that 
is provided in the UCSAS data challenge that includes data from major domestic and international 
gymnastic competitions from 2022 and 2023. I have opted against using the data from major domestic
and international gymnastic competions from 2017 to 2021 as time, injuries, 
and other factors can have a large impact on the success of a gymnast, so the greatest predictor
of the Olympic outcomes in 2024 will be the most recent data.
\\
For the purposes of my research design, when determining the most ideal feamle olympic candidates, 
I limited the data I utilized to only include female United States
gymnasts, presuming that the United States female gymnasts have a strong chance at earning medals in any category, 
based on the results of the 2020 Summer Olympics. When determining the most ideal American male candidates, 
I did inspect the data of non United States gymnasts in order to determine which medals the United States 
male team has the greatest chance of earning. 
Furthermore, I processed the data to remove any scores of zero based on the assumption that these may 
be indicative of missing scores and that instances of these scores are rare. I further justified my decision 
to eliminate scores of zero for the purposes of knowing the true mean scores of each athlete on each 
apparatus for each successful attempt. Additionally, for some athletes and competitions, I found that the vault
apparatus was listed as 'VT,' 'VT1,' and 'VT2.' This discrepancy is due to the fact that athletes are permitted
two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging 'VT,' 'VT1,' and 
'VT2' to all be reported as 'VT.' Also, the data source is flawed as it alternates between reporting athlete names
in upper or lower case letters. In order to correct this, I converted all last names to lower case for consistency 
purposes. Lastly, the data source is inconsistent in the manner that it reports the first names of athletes as certain
athletes are listed using only their first name at some competitions and are listed using their first and middle names 
under the 'first name' category for other competitions. In order to resolve this discrepancy, I manually verified that 
any athletes listed under two names were the same person and I further verified that there were no United States  
athletes with the same last name so that all statistical computations could be completed through grouping by last 
name alone.

>>>>

To predict which of the United States athletes are most likely to medal on the various apparatuses, 
I will be using the cleaned data that 
is provided in the UCSAS data challenge that includes data from major domestic and international 
gymnastic competitions from 2022 and 2023. I have opted against using the data from major domestic
and international gymnastic competions from 2017 to 2021 as time, injuries, 
and other factors can have a large impact on the success of a gymnast, so the greatest predictor
of the Olympic outcomes in 2024 will be the most recent data.
\\
For the purposes of my research design, when determining the most ideal feamle olympic candidates, 
I limited the data I utilized to only include female United States
gymnasts, presuming that the United States female gymnasts have a strong chance at earning medals in any category, 
based on the results of the 2020 Summer Olympics. When determining the most ideal American male candidates, 
I did inspect the data of non United States gymnasts in order to determine which medals the United States 
male team has the greatest chance of earning. 
Furthermore, I processed the data to remove any scores of zero based on the assumption that these may 
be indicative of missing scores and that instances of these scores are rare. I further justified my decision 
to eliminate scores of zero for the purposes of knowing the true mean scores of each athlete on each 
apparatus for each successful attempt. Additionally, for some athletes and competitions, I found that the vault
apparatus was listed as `VT,` `VT1,` and 'VT2.' This discrepancy is due to the fact that athletes are permitted
two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging 'VT,' 'VT1,' and 
'VT2' to all be reported as 'VT.' Also, the data source is flawed as it alternates between reporting athlete names
in upper or lower case letters. In order to correct this, I converted all last names to lower case for consistency 
purposes. Lastly, the data source is inconsistent in the manner that it reports the first names of athletes as certain
athletes are listed using only their first name at some competitions and are listed using their first and middle names 
under the 'first name' category for other competitions. In order to resolve this discrepancy, I manually verified that 
any athletes listed under two names were the same person and I further verified that there were no United States  
athletes with the same last name so that all statistical computations could be completed through grouping by last 
name alone.
